Ice sheet mass flows

### 2024-06-02 ms.tex
CRediT

\author[Mankoff and others]
       {Kenneth D. MANKOFF,$^{1,2}$
         William COLGAN,$^3$
         Xavier FETTWEIS,$^4$
         Someone, ELSE,$^n$}

\affiliation{%
  $^1$NASA Goddard Institute for Space Studies, New York, NY, 10025 USA\\
  $^2$Autonomic Integra LLC, New York, NY, 10025 USA\\
  $^3$GEUS affiliation\\
  $^4$Xavier affiliation\\
  $^n$Somewhere Else\\
  Correspondence: Ken Mankoff
  \email{ken.mankoff@nasa.gov}}

>>>>

\author[Mankoff and others]
       {Kenneth D. MANKOFF,$^{1,2}$
         Someone, ELSE,$^n$,
       add your name to CREDIT.CSV in repository}

\affiliation{%
  $^1$NASA Goddard Institute for Space Studies, New York, NY, 10025 USA\\
  $^2$Autonomic Integra LLC, New York, NY, 10025 USA\\
  $^n$Somewhere Else\\
  Correspondence: Ken Mankoff
  \email{ken.mankoff@nasa.gov}}
